---
title: "TURKOGLU_Malik"
output: html_document
date: "2026-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(questionr)
library(forcats)
library(ggplot2)
```
The commentaries in this document were originally in french, to make sure the code still works I kept the same name for the variables.
I) Introduction

Here, we're taking a look at a dataframe about a group of fish.
Thesere are the different variables:
Id: the identifier of the fish
Viscera.weight : the weight of the viscera of the fish
Diameter : diameter of the fish
Dim3: measurement of the fish on the third axis 

What we're trying to do is obtain linear regression models that allow to estimate Viscera.weight's value firstly, using
the Diameter, then using Dim3.


```{r}
donnees <- read.csv( file = "TURKOGLU_MALIK.csv",
                     sep =","  ,
                     dec ="."  ,
                     stringsAsFactors = TRUE)
```

II) Establish a linear model to estimate Viscera.weight with the Diameter




```{r}
resultat <- lm(formula = Viscera.weight~Diameter,
               data = donnees)
```
In order to get the results of the calculation of the lineary 
We put inside the variable resultat using the function lm the variable we want to explain and the explicative variable, it gives us 
the result of the calculation of the regression model

Now, we draw the scatter clount showing the evolution of Viscera.weight depending on the Diameter


```{r}
ggplot(
  data = donnees,
  mapping = aes(x = Diameter, y = Viscera.weight)
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle("évolution du poids des viscères en fonction du diamètre")+
  xlab("Diameter(mm)")+
  ylab("Viscera.weight(g)")
```

The line doesn't follow the evolution of Viscera.weight depending on the diameter. It seems more apporpriate to draw a curve here.

To get the curve, we will use FunctionModel

To start , we create two new variables , Viscera.weightLog and DiameterLog who will respectively contain  the results of the
Logarithmique function applied to Viscera.weight and Diameter

```{r}
donnees$Viscera.weightLog <- log10(donnees$Viscera.weight)
```


```{r}
donnees$DiameterLog <- log10(donnees$Diameter)
```

We use the function lm here again to calculate the new linear regression model


```{r}
res <-lm(formula = Viscera.weightLog~DiameterLog,
               data = donnees)
```

then, we draw the evolution of  viscera.weight depending on the diamer with the data at logaithimic scale


```{r}
ggplot(
  data = donnees,
  mapping = aes(x = DiameterLog, y = Viscera.weightLog)
  ) +
  geom_point() +
  geom_smooth( method = "lm", se = FALSE)+
  ggtitle("évolution du poids  en fonction du diamètre après transformation  logarithmique")+
  xlab("LogDiameter(mm)")+
  ylab("LogViscera.weight(g)")
```





Now, we take the original data and put them to logarithmic scale by applying the coefficient of the linear model of LogViscera.weight  depending on LogDiameter
```{r}
functionModel <- function(x){10^res$coefficients[1]*x^res$coefficients[2]}
ggplot(
  data = donnees,
  mapping = aes(x = Diameter, y = Viscera.weight)
  ) +
  geom_point() +
  geom_function(fun = functionModel, colour = "red")+
  ggtitle("évolution du poids en fonction du diamètre avec les données d'origine à l'échelle logarithmique")+
  xlab("Diameter(mm)")+
  ylab("Viscera.weight(g)")
```

Ce modèle semble  précis , les points sont autour de la courbe.

On peut poursuivre et calculer le modèle de régression.

This model seems accurate, the point are around the curve.

We can go on and calculate the regression model
```{r}
summary(res)
```





We have a coefficient of determination R² of 0.7031, he's higher than the p-value, which means it's valid and we can go on with this model.

R² is worth 0.7031 which means that 70.31% of the variance of Viscera.weightLog is explained by the variable DiameterLog.

Therefore, we have Viscera.weightLog = 1,7397*DiameterLog - 4.11.

We can say that each time DiameterLog goes up by 1 WeightLog goes up by 1.73.



III)  Estimating Viscera.weight using Dim3



Now, we studie the link between Dim3 and Viscera.weight.
To start, we calculate the linear regression model  of Viscera.weight depending on Dim3


```{r}
resultat2 <- lm(formula = Viscera.weight~Dim3,
                data = donnees)
```


Now, we draw the scatter plot that shows the evolution of the weight of the viscera depending on Dim3

```{r}

ggplot(
  data = donnees,
  mapping = aes(x = Dim3, y = Viscera.weight)
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle("évolution du poids des viscères en fonction de Dim3")+
  xlab("Dim3(mm)")+
  ylab("Viscera.weight(g)")
```

We can notice a tendancy, however the line doesn't follow it , we can try to erase the two values that seem really different compared to the rest


```{r}
 z <-subset(x = donnees, Dim3 < 930)
```

*We use the function Subset to delete the values that are too much bigger than the others to get a line that follows

the points tendency better.



```{r}
ggplot(
  data = z,
  mapping = aes(x = Dim3, y = Viscera.weight)
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle("évolution du poids en fonction de Dim3")+
  xlab("Dim3(mm)")+
  ylab("Viscera.weight(g)")
```

Après avoir enlevé les valeurs atypiques, on obtient un graphique avec  tous les points qui suivent l'allure de la

droite. 
After taking out the outilers, we get a graph with every points that follow the trajectory of the line


We calculate the linear regression model again without the outliers 

```{r}
res2 <-lm(formula = Viscera.weight~Dim3,
          data = z)
```




We print the summary of the new results

```{r}
summary(res2)
```

Here, R² is  worth 0.9221 which is higher than the p-value, so it's valid and we can continue the study.

R² being worth 0.9221,  we can say that 92.21% of the variance of Viscera.weight  is explained by Dim3.

We have Viscera.weight = Dim3 * 0.32672 - 5.52.

Every tim Dim3 goes up by 1 Viscera.weight goes up by 0,32.


IV) Conclusion

Finaly, we have two linear regression models who allow us to estimate the fish's weight of viscera:

Visceara.weightLog = 1,7397*DiameterLog - 4.11

And

Viscera.weight = Dim3*0,32672 -5,52  

These two models respectively got R² worth 70.31% and 92.21%.

The second's model R² being higher allows us to understand that getting an accurate idea of the weight of the viscera is
easier using Dim3 , since it explains a higher part of Viscera.weight's variance.





